---
title: " Predict Fuel Efficiency"
author: "Dibakar Ray"
date: "22 June 2016"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The prediction of Fuel efficiency is based on an underlying multiple linear regression model on mtcars dataset.  The underlying model is given below for information purpose.
```{r}
data("mtcars")
## View(mtcars)
#
#  Multiple Linear Regression
#
mfit = lm(mpg ~ wt + disp + cyl, data=mtcars)
summary(mfit)
```

## How to Use
A simple user interface is available to user who wants to find out or explore Fuel Efficiency (miles per gallon) for a given set of input - displacement, number of cylinders and weight of the car.
The user need to change the Displacement by clicking the Displacement  numeric input widget. The input will increase/decrease by 10 unit with each click.
Similarly, to provide a input of a different number of Cylinder, the user needs to click the 'Number of Cyliders'numericc input widget. Allowed values are 4, 6 and 8 cylinders.
In order to input weight of the car,user needs to use 'Weight'slider. Slider takes values from 1500 to 5500 Ibs.


```{r siderpanel, echo=FALSE}
    sidebarPanel(
        
        
        h3('How to Use'),
           
           c('Please enter :.'),
        numericInput('disp', 'Displacement:',70, min = 50, max = 500, step = 10), 
        numericInput('cyldr', 'Number of cylinders (4,6,8):', 4, min = 4, max = 8, step = 2),
        sliderInput('wght', 'Weight (lbs):',1500, min = 1500, max = 5500, step = 100)
    )
   

```

As the Inputs are  changed  on the side panel the user can see  on the main panel changed inputs and the predicted Fuel efficinecy in miles per gallon for the new input set.

```{r mainpanel, echo=FALSE}
 data(mtcars)

mfit = lm(mpg ~ wt + disp + cyl, data=mtcars)
weight <- reactive({input$wght/1000})
displacement <- reactive(input$disp)
cylinder <- reactive(input$cyldr)
predicted_mpg <-reactive({mfit$coefficients[1] + mfit$coefficients[2] * weight() + mfit$coefficients[3] * displacement() + mfit$coefficients[4] * cylinder()})

        renderText({'Predicted Fuel Efficiency (MPG)'})
        renderText({'Predict for:'})
        renderText({paste(input$disp, "displacement, ",
                                                 input$cyldr, "cylinders, ",
                                                 input$wght, "weight")})
        renderText({'Fuel efficiency (MPG):'})
        renderText({paste(round(predicted_mpg(), 2), "MPG")})

   
 
        
        


      



```



